### 2010-10-01 doc/guide/quickstart.tex
- updated language section
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/trunk/gringo@3394 3e02f596-3131-0410-8352-e04eeaec37cc
fixed typo
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/trunk/gringo@3428 3e02f596-3131-0410-8352-e04eeaec37cc

We consider a Towers of Hanoi instance specified via facts over predicates
\pred{peg}/$1$ and \pred{disk}/$1$ that correspond to the pegs and disks in the puzzle.
Discs are enumerated by consecutive integers beginning with one
where a disc with a lower number is considered to be bigger than a list with a higher number.
The pegs can have arbitrary names. 
Furthermore, the predicates \pred{init\_on}/$2$ and \pred{goal\_on}/$2$ describe the initial and goal situation, respectively.
Their first argument is the number of a disc and the second argument is the peg 
on which the disc is located in the initial or goal situation.
Finally, the predicate \pred{moves}/$1$ specifies the number of moves within which the goal situation has to be reached.
Note that the original puzzle had exactly three pegs and a fixed initial and goal situation.
With ASP we can easily change this requirement and 
the encoding represented in the following works with an arbitrary number of pegs and any initial or goal situation.
Figure~\ref{fig:toh_inst} depicts a possible instance (the dashed discs mark the goal situation) 
corresponding to the ASP program given below.

@@

The `\code{;}' in the first line is some syntactic sugar (Section \ref{subsec:gringo:pool})
that expands the statement into three facts
\code{peg(a)}, \code{peg(b)}, and \code{peg(c)} representing the three pegs.
Again, in the second line some syntactic sugar is used to 
create the facts \code{disc(1)}, \code{disc(2)}, \code{disc(3)}, and \code{disc(4)}.
Here the term \code{1..4}, an intervall (Section \ref{subsec:gringo:interval}), is successively replaced by \code{1}, \code{2}, \code{3}, and \code{4}.
The initial and goal situation is specified in line three and four again using intervall.
Finally, in the last line the number of moves to solve the problem is given.

>>>>

We consider a Towers of Hanoi instance specified via facts over predicates
\pred{peg}/$1$ and \pred{disk}/$1$ that correspond to the pegs and disks in the puzzle.
Discs are enumerated by consecutive integers beginning with one
where a disc with a lower number is considered to be bigger than a disc with a higher number.
The pegs can have arbitrary names. 
Furthermore, the predicates \pred{init\_on}/$2$ and \pred{goal\_on}/$2$ describe the initial and goal situation, respectively.
Their first argument is the number of a disc and the second argument is the peg 
on which the disc is located in the initial or goal situation.
Finally, the predicate \pred{moves}/$1$ specifies the number of moves within which the goal situation has to be reached.
Note that the original puzzle had exactly three pegs and a fixed initial and goal situation.
With ASP we can easily change this requirement and 
the encoding represented in the following works with an arbitrary number of pegs and any initial or goal situation.
Figure~\ref{fig:toh_inst} depicts a possible instance (the dashed discs mark the goal situation) 
corresponding to the ASP program given below.

@@

The ``\code{;}'' in the first line is some syntactic sugar (Section \ref{subsec:gringo:pool})
that expands the statement into three facts
\code{peg(a)}, \code{peg(b)}, and \code{peg(c)} representing the three pegs.
Again, in the second line some syntactic sugar is used to 
create the facts \code{disc(1)}, \code{disc(2)}, \code{disc(3)}, and \code{disc(4)}.
Here the term \code{1..4}, an intervall (Section \ref{subsec:gringo:interval}), is successively replaced by \code{1}, \code{2}, \code{3}, and \code{4}.
The initial and goal situation is specified in line three and four again using intervall.
Finally, in the last line the number of moves to solve the problem is given.
